Optimal Task Phasing for End-To-End Latency in Harmonic Systems and Semi-Harmonic Automotive Systems

### 2024-09-27 paper.tex
minor

	\maketitle

@@

	As the motivating example demonstrates, there is a high potential of reducing the end-to-end latency by modifying the task phases. 
	In this section, we
	consider a cause-effect chain 
	\begin{equation}
		E = (\tau_1 \to\dots\to \tau_n),
	\end{equation}
	and
	explore optimal task phasing 
	that minimizes $\lat(E)$ if the system is harmonic.
	Actually, the results of this section work even for a larger class of task systems, in which the tasks 
	\begin{equation}
		\Tbb_E := \setof{\tau_1, \dots, \tau_n} \subseteq \Tbb
	\end{equation}
	of the cause-effect chain $E$ are \emph{max-harmonic}.

@@

		\textbf{Base case} ($i=p$):
		By definition, $j'_i = 1 = \frac{T_{\tau_p}}{T_{\tau_i}}$.
		Hence, Equation~\eqref{eq:induction_thm} holds for $i=p$.

@@

		We conclude that 
		\begin{math}
			\ell(\pc^p_0) 
			= \we(\tau_n(j'_n)) - \re(\tau_1(j_1)) 
			= \we\left(\tau_n\left(\frac{T_{\tau_p}}{T_{\tau_n}}\right)\right) - \re(\tau_1(0)) 
			= \phi_{\tau_n} + \left(\frac{T_{\tau_p}}{T_{\tau_n}} +1 \right) \cdot T_{\tau_n} - \phi_{\tau_1}
			= \sum_{\xi=1}^{n-1} T_{\tau_\xi} + T_{\tau_p} + T_{\tau_n} - 0
			= \sum_{\xi=1}^{n} T_{\tau_\xi} + T_{\tau_p}.
		\end{math}
		% \begin{align}
		% 	\ell(\pc^p_0) 
		% 	&= \we(\tau_n(j'_n)) - \re(\tau_1(j_1)) 
		% 	= \we\left(\tau_n\left(\frac{T_{\tau_p}}{T_{\tau_n}}\right)\right) - \re(\tau_1(0)) 
		% 	\\& = \phi_{\tau_n} + \left(\frac{T_{\tau_p}}{T_{\tau_n}} +1 \right) \cdot T_{\tau_n} - \phi_{\tau_1}
		% 	= \sum_{\xi=1}^{n-1} T_{\tau_\xi} + T_{\tau_p} + T_{\tau_n} - 0
		% 	= \sum_{\xi=1}^{n} T_{\tau_\xi} + T_{\tau_p}.
		% \end{align}
		Hence, the latency is 
		$\lat(E) = \ell(\pc^p_0) = \sum_{i=1}^{n} T_{\tau_i} + T_{\tau_p} = \sum_{i=1}^{n} T_{\tau_i} + \max_{i=1, \dots, n} T_{\tau_i}$.
	\end{proof}

>>>>

	\maketitle
	\thispagestyle{plain}
	\pagestyle{plain}

@@

	As the motivating example demonstrates, there is a high potential of reducing the end-to-end latency by modifying the task phases. 
	In this section, we
	consider a cause-effect chain 
	\begin{math}
		E = (\tau_1 \to\dots\to \tau_n),
	\end{math}
	and
	explore optimal task phasing 
	that minimizes $\lat(E)$ if the system is harmonic.
	Actually, the results of this section work even for a larger class of task systems, in which the tasks 
	\begin{math}
		\Tbb_E = \setof{\tau_1, \dots, \tau_n}
	\end{math}
	of the cause-effect chain $E$ are \emph{max-harmonic}.

@@

		\smallskip
		\textbf{Base case} ($i=p$):
		By definition, $j'_i = 1 = \frac{T_{\tau_p}}{T_{\tau_i}}$.
		Hence, Equation~\eqref{eq:induction_thm} holds for $i=p$.

@@

		\smallskip
		We conclude that 
		\begin{math}
			\ell(\pc^p_0) 
			= \we(\tau_n(j'_n)) - \re(\tau_1(j_1)) 
			= \we\left(\tau_n\left(\frac{T_{\tau_p}}{T_{\tau_n}}\right)\right) - \re(\tau_1(0)) 
			= \phi_{\tau_n} + \left(\frac{T_{\tau_p}}{T_{\tau_n}} +1 \right) \cdot T_{\tau_n} - \phi_{\tau_1}
			= \sum_{\xi=1}^{n-1} T_{\tau_\xi} + T_{\tau_p} + T_{\tau_n} - 0
			= \sum_{\xi=1}^{n} T_{\tau_\xi} + T_{\tau_p}.
		\end{math}
		% \begin{align}
		% 	\ell(\pc^p_0) 
		% 	&= \we(\tau_n(j'_n)) - \re(\tau_1(j_1)) 
		% 	= \we\left(\tau_n\left(\frac{T_{\tau_p}}{T_{\tau_n}}\right)\right) - \re(\tau_1(0)) 
		% 	\\& = \phi_{\tau_n} + \left(\frac{T_{\tau_p}}{T_{\tau_n}} +1 \right) \cdot T_{\tau_n} - \phi_{\tau_1}
		% 	= \sum_{\xi=1}^{n-1} T_{\tau_\xi} + T_{\tau_p} + T_{\tau_n} - 0
		% 	= \sum_{\xi=1}^{n} T_{\tau_\xi} + T_{\tau_p}.
		% \end{align}
		Hence, the latency is 
		$\lat(E) = \ell(\pc^p_0) = \sum_{i=1}^{n} T_{\tau_i} + T_{\tau_p} = \sum_{i=1}^{n} T_{\tau_i} + \max_{i=1, \dots, n} T_{\tau_i}$.
	\end{proof}
